### 2017-08-31 Paper/Threshold/Compare.tex
Test F1 score for different threshold formulea.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                      & \multicolumn{5}{c|}{2nd Order}                               \\ \hline
				& TP & FP  & TN  & FN                        & F1 Score                               & TP & FP  & TN  & FN & F1 Score                               \\ \hline
				& 34 & 172 & 89  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2833}} & 37 & 111 & 146 & 1  & {\color[HTML]{FE0000} \textbf{0.3978}} \\ \cline{2-11} 
				& 33 & 166 & 96  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2845}} & 39 & 141 & 115 & 0  & {\color[HTML]{FE0000} \textbf{0.3562}} \\ \cline{2-11} 
				& 23 & 178 & 94  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2054}} & 27 & 122 & 146 & 0  & {\color[HTML]{FE0000} \textbf{0.3068}} \\ \cline{2-11} 
				& 31 & 148 & 116 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2952}} & 34 & 116 & 145 & 0  & {\color[HTML]{FE0000} \textbf{0.3696}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 26 & 173 & 96  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2311}} & 34 & 146 & 115 & 0  & {\color[HTML]{FE0000} \textbf{0.3178}} \\ \hline
				& 18 & 168 & 99  & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.1682}} & 25 & 134 & 136 & 0  & {\color[HTML]{FE0000} \textbf{0.2717}} \\ \cline{2-11} 
				& 17 & 170 & 99  & {\color[HTML]{333333} 9}  & {\color[HTML]{FE0000} \textbf{0.1596}} & 31 & 136 & 128 & 0  & {\color[HTML]{FE0000} \textbf{0.3131}} \\ \cline{2-11} 
				& 14 & 161 & 108 & {\color[HTML]{333333} 12} & {\color[HTML]{FE0000} \textbf{0.1393}} & 30 & 140 & 125 & 0  & {\color[HTML]{FE0000} \textbf{0.3000}} \\ \cline{2-11} 
				& 25 & 157 & 98  & {\color[HTML]{333333} 15} & {\color[HTML]{FE0000} \textbf{0.2252}} & 28 & 115 & 152 & 0  & {\color[HTML]{FE0000} \textbf{0.3275}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 18 & 145 & 117 & {\color[HTML]{333333} 15} & {\color[HTML]{FE0000} \textbf{0.1837}} & 23 & 136 & 136 & 0  & {\color[HTML]{FE0000} \textbf{0.2527}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 30 & 6  & 259 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9091}} & 20 & 48 & 227 & 0  & {\color[HTML]{FE0000} \textbf{0.4545}} \\ \cline{2-11} 
				& 35 & 8  & 252 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8974}} & 24 & 25 & 246 & 0  & {\color[HTML]{FE0000} \textbf{0.6575}} \\ \cline{2-11} 
				& 27 & 7  & 261 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8852}} & 30 & 48 & 217 & 0  & {\color[HTML]{FE0000} \textbf{0.5556}} \\ \cline{2-11} 
				& 36 & 6  & 253 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9231}} & 33 & 48 & 214 & 0  & {\color[HTML]{FE0000} \textbf{0.5789}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 23 & 7  & 256 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8679}} & 32 & 48 & 215 & 0  & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \hline
				& 7  & 73 & 194 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.1296}} & 33 & 23 & 239 & 0  & {\color[HTML]{FE0000} \textbf{0.7416}} \\ \cline{2-11} 
				& 11 & 68 & 190 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.1897}} & 27 & 45 & 223 & 0  & {\color[HTML]{FE0000} \textbf{0.5455}} \\ \cline{2-11} 
				& 10 & 90 & 171 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.1493}} & 27 & 66 & 202 & 0  & {\color[HTML]{FE0000} \textbf{0.4500}} \\ \cline{2-11} 
				& 9  & 81 & 181 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.1463}} & 31 & 30 & 234 & 0  & {\color[HTML]{FE0000} \textbf{0.6739}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 5  & 83 & 193 & {\color[HTML]{333333} 14} & {\color[HTML]{FE0000} \textbf{0.0935}} & 24 & 46 & 225 & 0  & {\color[HTML]{FE0000} \textbf{0.5106}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 13 & 2  & 264 & {\color[HTML]{333333} 16} & {\color[HTML]{FE0000} \textbf{0.5909}} & 23 & 24 & 246 & 2  & {\color[HTML]{FE0000} \textbf{0.6389}} \\ \cline{2-11} 
				& 10 & 2  & 270 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.5714}} & 24 & 16 & 250 & 5  & {\color[HTML]{FE0000} \textbf{0.6957}} \\ \cline{2-11} 
				& 29 & 2  & 242 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.7073}} & 23 & 24 & 245 & 3  & {\color[HTML]{FE0000} \textbf{0.6301}} \\ \cline{2-11} 
				& 14 & 2  & 262 & {\color[HTML]{333333} 17} & {\color[HTML]{FE0000} \textbf{0.5957}} & 23 & 32 & 234 & 1  & {\color[HTML]{FE0000} \textbf{0.6292}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 14 & 1  & 263 & {\color[HTML]{333333} 17} & {\color[HTML]{FE0000} \textbf{0.6087}} & 21 & 23 & 248 & 3  & {\color[HTML]{FE0000} \textbf{0.6176}} \\ \hline
				& 1  & 13 & 260 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.0556}} & 35 & 9  & 250 & 1  & {\color[HTML]{FE0000} \textbf{0.8750}} \\ \cline{2-11} 
				& 1  & 13 & 260 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.0556}} & 22 & 5  & 267 & 1  & {\color[HTML]{FE0000} \textbf{0.8800}} \\ \cline{2-11} 
				& 2  & 12 & 254 & {\color[HTML]{333333} 17} & {\color[HTML]{FE0000} \textbf{0.0930}} & 27 & 2  & 261 & 5  & {\color[HTML]{FE0000} \textbf{0.8852}} \\ \cline{2-11} 
				& 5  & 13 & 246 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.1852}} & 33 & 8  & 253 & 1  & {\color[HTML]{FE0000} \textbf{0.8800}}  \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 3  & 13 & 253 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.1333}} & 26 & 6  & 261 & 2  & {\color[HTML]{FE0000} \textbf{0.8667}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 21 & 1  & 260 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.7500}} & 29 & 26 & 240 & 0  & {\color[HTML]{FE0000} \textbf{0.6905}} \\ \cline{2-11} 
				& 15 & 1  & 267 & {\color[HTML]{333333} 12} & {\color[HTML]{FE0000} \textbf{0.6977}} & 28 & 41 & 221 & 5  & {\color[HTML]{FE0000} \textbf{0.5490}} \\ \cline{2-11} 
				& 9  & 2  & 263 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.4390}} & 29 & 14 & 249 & 3  & {\color[HTML]{FE0000} \textbf{0.7733}} \\ \cline{2-11} 
				& 11 & 2  & 264 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.5238}} & 28 & 28 & 236 & 3  & {\color[HTML]{FE0000} \textbf{0.6437}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 8  & 2  & 274 & {\color[HTML]{333333} 11} & {\color[HTML]{FE0000} \textbf{0.5517}} & 31 & 18 & 243 & 3  & {\color[HTML]{FE0000} \textbf{0.7470}} \\ \hline
				& 1  & 16 & 249 & {\color[HTML]{333333} 29} & {\color[HTML]{FE0000} \textbf{0.0426}} & 21 & 11 & 263 & 0  & {\color[HTML]{FE0000} \textbf{0.7925}} \\ \cline{2-11} 
				& 5  & 10 & 249 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.1961}} & 24 & 15 & 256 & 0  & {\color[HTML]{FE0000} \textbf{0.7619}} \\ \cline{2-11} 
				& 1  & 18 & 250 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0435}} & 35 & 8  & 252 & 0  & {\color[HTML]{FE0000} \textbf{0.8974}} \\ \cline{2-11} 
				& 2  & 13 & 243 & {\color[HTML]{333333} 37} & {\color[HTML]{FE0000} \textbf{0.0741}} & 25 & 5  & 263 & 2  & {\color[HTML]{FE0000} \textbf{0.8772}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 3  & 12 & 250 & {\color[HTML]{333333} 30} & {\color[HTML]{FE0000} \textbf{0.1250}} & 32 & 4  & 253 & 6  & {\color[HTML]{FE0000} \textbf{0.8649}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 11 & 2  & 263 & {\color[HTML]{333333} 19} & {\color[HTML]{FE0000} \textbf{0.5116}} & 25 & 20 & 248 & 2  & {\color[HTML]{FE0000} \textbf{0.6944}} \\ \cline{2-11} 
				& 7  & 1  & 262 & {\color[HTML]{333333} 25} & {\color[HTML]{FE0000} \textbf{0.3500}} & 25 & 18 & 250 & 2  & {\color[HTML]{FE0000} \textbf{0.7143}} \\ \cline{2-11} 
				& 11 & 2  & 272 & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.6471}} & 29 & 16 & 248 & 2  & {\color[HTML]{FE0000} \textbf{0.7632}} \\ \cline{2-11} 
				& 11 & 2  & 264 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.5238}} & 23 & 20 & 244 & 8  & {\color[HTML]{FE0000} \textbf{0.6216}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 15 & 2  & 248 & {\color[HTML]{333333} 30} & {\color[HTML]{FE0000} \textbf{0.4839}} & 27 & 20 & 242 & 6  & {\color[HTML]{FE0000} \textbf{0.6750}} \\ \hline
				& 2  & 12 & 253 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.0909}} & 25 & 4  & 264 & 2  & {\color[HTML]{FE0000} \textbf{0.8929}} \\ \cline{2-11} 
				& 0  & 17 & 249 & {\color[HTML]{333333} 29} & {\color[HTML]{FE0000} \textbf{0.0000}} & 28 & 11 & 255 & 1  & {\color[HTML]{FE0000} \textbf{0.8235}} \\ \cline{2-11} 
				& 1  & 13 & 250 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.0435}} & 23 & 4  & 263 & 5  & {\color[HTML]{FE0000} \textbf{0.8364}} \\ \cline{2-11} 
				& 2  & 14 & 254 & {\color[HTML]{333333} 25} & {\color[HTML]{FE0000} \textbf{0.0930}} & 21 & 5  & 267 & 2  & {\color[HTML]{FE0000} \textbf{0.8571}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 1  & 13 & 261 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.0571}} & 25 & 1  & 266 & 3  & {\color[HTML]{FE0000} \textbf{0.9259}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP  & TN & FN                        & F1 Score                               & TP & FP  & TN & FN & F1 Score                               \\ \hline
				& 34 & 202 & 59 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2519}} & 29 & 222 & 44 & 0  & {\color[HTML]{FE0000} \textbf{0.2071}} \\ \cline{2-11} 
				& 30 & 202 & 63 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2290}} & 33 & 217 & 45 & 0  & {\color[HTML]{FE0000} \textbf{0.2332}} \\ \cline{2-11} 
				& 24 & 216 & 55 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.1818}} & 33 & 216 & 46 & 0  & {\color[HTML]{FE0000} \textbf{0.2340}} \\ \cline{2-11} 
				& 31 & 201 & 63 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2357}} & 33 & 216 & 46 & 0  & {\color[HTML]{FE0000} \textbf{0.2340}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 36 & 202 & 57 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2628}} & 40 & 207 & 48 & 0  & {\color[HTML]{FE0000} \textbf{0.2787}} \\ \hline
				& 23 & 208 & 55 & {\color[HTML]{333333} 9}  & {\color[HTML]{FE0000} \textbf{0.1749}} & 25 & 228 & 42 & 0  & {\color[HTML]{FE0000} \textbf{0.1799}} \\ \cline{2-11} 
				& 20 & 206 & 59 & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.1563}} & 25 & 225 & 45 & 0  & {\color[HTML]{FE0000} \textbf{0.1818}} \\ \cline{2-11} 
				& 22 & 203 & 65 & {\color[HTML]{333333} 5}  & {\color[HTML]{FE0000} \textbf{0.1746}} & 17 & 234 & 44 & 0  & {\color[HTML]{FE0000} \textbf{0.1269}} \\ \cline{2-11} 
				& 15 & 217 & 55 & {\color[HTML]{333333} 8}  & {\color[HTML]{FE0000} \textbf{0.1176}} & 34 & 220 & 41 & 0  & {\color[HTML]{FE0000} \textbf{0.2361}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 22 & 210 & 53 & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.1667}} & 23 & 228 & 44 & 0  & {\color[HTML]{FE0000} \textbf{0.1679}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                    & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP  & TN & FN                       & F1 Score                               & TP & FP  & TN & FN & F1 Score                               \\ \hline
				& 33 & 193 & 63 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.2548}} & 28 & 219 & 48 & 0  & {\color[HTML]{FE0000} \textbf{0.2036}} \\ \cline{2-11} 
				& 24 & 199 & 72 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.1943}} & 36 & 207 & 52 & 0  & {\color[HTML]{FE0000} \textbf{0.2581}} \\ \cline{2-11} 
				& 38 & 183 & 74 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.2934}} & 36 & 206 & 53 & 0  & {\color[HTML]{FE0000} \textbf{0.2590}} \\ \cline{2-11} 
				& 25 & 201 & 69 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.1992}} & 35 & 205 & 55 & 0  & {\color[HTML]{FE0000} \textbf{0.2545}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 28 & 199 & 68 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.2196}} & 26 & 216 & 53 & 0  & {\color[HTML]{FE0000} \textbf{0.1940}} \\ \hline
				& 26 & 190 & 76 & {\color[HTML]{333333} 3} & {\color[HTML]{FE0000} \textbf{0.2122}} & 22 & 224 & 49 & 0  & {\color[HTML]{FE0000} \textbf{0.1642}} \\ \cline{2-11} 
				& 17 & 201 & 70 & {\color[HTML]{333333} 7} & {\color[HTML]{FE0000} \textbf{0.1405}} & 25 & 222 & 48 & 0  & {\color[HTML]{FE0000} \textbf{0.1838}} \\ \cline{2-11} 
				& 22 & 191 & 77 & {\color[HTML]{333333} 5} & {\color[HTML]{FE0000} \textbf{0.1833}} & 26 & 220 & 49 & 0  & {\color[HTML]{FE0000} \textbf{0.1912}} \\ \cline{2-11} 
				& 16 & 200 & 73 & {\color[HTML]{333333} 6} & {\color[HTML]{FE0000} \textbf{0.1345}} & 26 & 224 & 45 & 0  & {\color[HTML]{FE0000} \textbf{0.1884}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 17 & 202 & 71 & {\color[HTML]{333333} 5} & {\color[HTML]{FE0000} \textbf{0.1411}} & 29 & 219 & 47 & 0  & {\color[HTML]{FE0000} \textbf{0.2094}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 6  & 2  & 267 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.3750}} & 7  & 5  & 264 & 19 & {\color[HTML]{FE0000} \textbf{0.3684}} \\ \cline{2-11} 
				& 10 & 2  & 270 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.5714}} & 7  & 4  & 263 & 21 & {\color[HTML]{FE0000} \textbf{0.3590}} \\ \cline{2-11} 
				& 8  & 1  & 262 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.3902}} & 12 & 5  & 265 & 13 & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \cline{2-11} 
				& 11 & 1  & 259 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.4681}} & 7  & 4  & 263 & 21 & {\color[HTML]{FE0000} \textbf{0.3590}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 12 & 1  & 262 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.5333}} & 12 & 2  & 265 & 16 & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \hline
				& 0  & 11 & 252 & {\color[HTML]{333333} 32} & {\color[HTML]{FE0000} \textbf{0.0000}} & 12 & 0  & 262 & 21 & {\color[HTML]{FE0000} \textbf{0.5333}} \\ \cline{2-11} 
				& 0  & 11 & 253 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.0000}} & 10 & 0  & 270 & 15 & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \cline{2-11} 
				& 1  & 12 & 258 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.0526}} & 18 & 0  & 254 & 23 & {\color[HTML]{FE0000} \textbf{0.6101}} \\ \cline{2-11} 
				& 2  & 9  & 261 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.1111}} & 10 & 0  & 267 & 18 & {\color[HTML]{FE0000} \textbf{0.5263}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 2  & 9  & 257 & {\color[HTML]{333333} 27} & {\color[HTML]{FE0000} \textbf{0.1000}} & 13 & 0  & 260 & 22 & {\color[HTML]{FE0000} \textbf{0.5417}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 24 & 2  & 266 & {\color[HTML]{333333} 3}  & {\color[HTML]{FE0000} \textbf{0.9057}} & 19 & 12 & 252 & 12 & {\color[HTML]{FE0000} \textbf{0.6129}} \\ \cline{2-11} 
				& 28 & 3  & 264 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9492}} & 29 & 14 & 248 & 4  & {\color[HTML]{FE0000} \textbf{0.7632}} \\ \cline{2-11} 
				& 27 & 4  & 264 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9310}} & 23 & 14 & 253 & 5  & {\color[HTML]{FE0000} \textbf{0.7077}} \\ \cline{2-11} 
				& 26 & 3  & 265 & {\color[HTML]{333333} 1}  & {\color[HTML]{FE0000} \textbf{0.9286}} & 17 & 13 & 256 & 9  & {\color[HTML]{FE0000} \textbf{0.6071}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 31 & 4  & 257 & {\color[HTML]{333333} 3}  & {\color[HTML]{FE0000} \textbf{0.8986}} & 18 & 14 & 257 & 6  & {\color[HTML]{FE0000} \textbf{0.6429}} \\ \hline
				& 8  & 25 & 242 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.2623}} & 24 & 10 & 261 & 0  & {\color[HTML]{FE0000} \textbf{0.8276}} \\ \cline{2-11} 
				& 4  & 27 & 243 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.1429}} & 30 & 6  & 258 & 1  & {\color[HTML]{FE0000} \textbf{0.8955}} \\ \cline{2-11} 
				& 3  & 32 & 239 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.1017}} & 34 & 9  & 252 & 0  & {\color[HTML]{FE0000} \textbf{0.8831}} \\ \cline{2-11} 
				& 4  & 29 & 229 & {\color[HTML]{333333} 33} & {\color[HTML]{FE0000} \textbf{0.1143}} & 20 & 1  & 262 & 12 & {\color[HTML]{FE0000} \textbf{0.7547}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 1  & 33 & 235 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0328}} & 34 & 2  & 257 & 2  & {\color[HTML]{FE0000} \textbf{0.9444}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 11 & 1  & 262 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.5000}} & 8  & 5  & 259 & 23 & {\color[HTML]{FE0000} \textbf{0.3636}} \\ \cline{2-11} 
				& 5  & 1  & 266 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.2941}} & 9  & 3  & 271 & 12 & {\color[HTML]{FE0000} \textbf{0.5455}} \\ \cline{2-11} 
				& 6  & 2  & 264 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.3243}} & 10 & 2  & 267 & 16 & {\color[HTML]{FE0000} \textbf{0.5263}} \\ \cline{2-11} 
				& 6  & 1  & 270 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.3871}} & 16 & 3  & 256 & 20 & {\color[HTML]{FE0000} \textbf{0.5818}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 7  & 0  & 267 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.4000}} & 9  & 6  & 261 & 19 & {\color[HTML]{FE0000} \textbf{0.4186}} \\ \hline
				& 0  & 11 & 262 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.0000}} & 17 & 0  & 254 & 24 & {\color[HTML]{FE0000} \textbf{0.5862}} \\ \cline{2-11} 
				& 1  & 9  & 257 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.0513}} & 6  & 0  & 269 & 20 & {\color[HTML]{FE0000} \textbf{0.3750}} \\ \cline{2-11} 
				& 1  & 10 & 258 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0526}} & 13 & 0  & 264 & 18 & {\color[HTML]{FE0000} \textbf{0.5909}} \\ \cline{2-11} 
				& 0  & 12 & 255 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.0000}} & 15 & 0  & 255 & 25 & {\color[HTML]{FE0000} \textbf{0.5455}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 1  & 10 & 238 & {\color[HTML]{333333} 46} & {\color[HTML]{FE0000} \textbf{0.0345}} & 13 & 0  & 264 & 18 & {\color[HTML]{FE0000} \textbf{0.5909}} \\ \hline
			\end{tabular}
		\end{table}

@@

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
				& 25 & 2  & 256 & {\color[HTML]{333333} 12} & {\color[HTML]{FE0000} \textbf{0.7813}} & 22 & 17 & 250 & 6  & {\color[HTML]{FE0000} \textbf{0.6567}} \\ \cline{2-11} 
				& 15 & 2  & 260 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.6000}} & 23 & 23 & 247 & 2  & {\color[HTML]{FE0000} \textbf{0.6479}} \\ \cline{2-11} 
				& 12 & 1  & 262 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.5333}} & 24 & 15 & 250 & 6  & {\color[HTML]{FE0000} \textbf{0.6957}} \\ \cline{2-11} 
				& 13 & 2  & 267 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.6341}} & 28 & 27 & 235 & 5  & {\color[HTML]{FE0000} \textbf{0.6364}} \\ \cline{2-11} 
				\multirow{-5}{*}{Centralized} & 12 & 0  & 272 & {\color[HTML]{333333} 11} & {\color[HTML]{FE0000} \textbf{0.6857}} & 21 & 29 & 242 & 3  & {\color[HTML]{FE0000} \textbf{0.5676}} \\ \hline
				& 2  & 12 & 256 & {\color[HTML]{333333} 25} & {\color[HTML]{FE0000} \textbf{0.0976}} & 20 & 3  & 270 & 2  & {\color[HTML]{FE0000} \textbf{0.8889}} \\ \cline{2-11} 
				& 2  & 12 & 238 & {\color[HTML]{333333} 43} & {\color[HTML]{FE0000} \textbf{0.0678}} & 43 & 7  & 244 & 1  & {\color[HTML]{FE0000} \textbf{0.9149}} \\ \cline{2-11} 
				& 3  & 11 & 244 & {\color[HTML]{333333} 37} & {\color[HTML]{FE0000} \textbf{0.1111}} & 16 & 1  & 276 & 2  & {\color[HTML]{FE0000} \textbf{0.9143}} \\ \cline{2-11} 
				& 0  & 17 & 245 & {\color[HTML]{333333} 33} & {\color[HTML]{FE0000} \textbf{0.0000}} & 29 & 7  & 259 & 0  & {\color[HTML]{FE0000} \textbf{0.8923}} \\ \cline{2-11} 
				\multirow{-5}{*}{Equalized}   & 3  & 11 & 259 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.1538}} & 27 & 5  & 261 & 2  & {\color[HTML]{FE0000} \textbf{0.8852}} \\ \hline
			\end{tabular}
		\end{table}
